Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Finish Slides

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of measurements \(N_m\).
Here, we consider
%
\Disp{
N_p \gg N_m
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

\Result
{Definition}
{
We say \(T (N_m) =\{1, \dotsc, N_m\}\), \(N_m \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N_m)\).
}

@@

\Result
{Definition}
{
\(h \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
%
\Disp{ 
x_{T (N) -\MC{A}} =\V{0}
}
with
\Disp{ 
\# \MC{A} \leq s.
}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

@@

\Result
{Definition}
{
Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \d_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
%
\Disp{
(1-\d_s) \|h\|^2
\leq \|P_{\MB{T}} h\|_2^2
\leq (1+\d_s) \|h\|^2
}
}

RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\d_s\).

Consider a linear transformation with noise corruption,
%
\Disp{
\V{y} =\M{P} \V{h} + \V{z}
}
%
where (w.l.o.g.) \(z\) is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

@@

And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
Note that they confined their discussion for real vectors.

@@

Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.

Same as before, consider \(\V{y} \in \MB{V}_\MB{K} (N_p)\), \(\V{h} \in \MB{V}_\MB{K} (N_s)\), where \(\V{h}\) is \(s\)-sparse, with \(N_p \gg N_s\).
If
\Disp{
\V{y} =\M{P} \M{h},
}
that is, the noiseless, real-number case.
We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\).

@@

\begin{enumerate}
\item Previous work favors OMP rather than DS, let alone other sparse algorithm.
\item Previous work simply assumes the bound of the norm of the channel matrix.
\item The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian (Tropp and Gilvert 2007) seems to be more restrictive than RIP (Cand\`es and Tao 2007).
\item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.
\end{enumerate}

>>>>

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p \in \MB{N}\) is much larger than the number of measurements \(N_m \in \MB{N}\), namely,
%
\Disp{
N_p \gg N_m
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

We will use \(T (N_m) =\{1, \dotsc, N_m\}\) to denote the support of \(\MB{V}_{\MB{K}} (N_m)\).

@@

\Result
{Definition}
{
\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
%
\Disp{ 
x_{T (N) -\MC{A}} =\V{0}
}
with
\Disp{ 
\# \MC{A} \leq s.
}
That is, only at most \(s\) components of \(x\) is nonzero.
}

@@

\Result
{Definition}
{
Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset T(N_m)\) with \(\#\{\MC{T}\} \leq s\),
%
\Disp{
(1-\d_s) \|\V{x}\|^2
\leq \|P_{\MC{T}} \V{x}\|_2^2
\leq (1+\d_s) \|\V{x}\|_2^2
}
}

RIP is essentially saying that \(P\) is ``almost unitary'' up to ``relative error'' \(\d_s\).

Now, consider a linear transformation with noise corruption,
%
\Disp{
\V{y} =\M{P} \V{h} + \V{z}
}
%
where (w.l.o.g.) \(z\) is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

@@

They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
Note that they confined their discussion for real vectors.

@@

Around that time, Tropp and Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit (OMP), that an i.i.d.\ random matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.

Same as before, consider \(\V{y} \in \MB{V}_\MB{K} (N_p)\), \(\V{h} \in \MB{V}_\MB{K} (N_s)\), where \(\V{h}\) is \(s\)-sparse, with \(N_p \gg N_s\).
If
\Disp{
\V{y} =\M{P} \M{h},
}
that is, the noiseless, real-number case.
We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.

@@

\begin{enumerate}
\item Previous work favors OMP rather than DS, let alone other sparse algorithm.
\item Previous work simply assumes the bound of the norm of the channel matrix.
\item The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian (Tropp and Gilvert 2007) seems to be more restrictive than RIP (Cand\`es and Tao 2007).
\item The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
\item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.
\end{enumerate}
